Title

### 2014-01-17 paper/parts/methods.tex

We can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). This is the view of a user's dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}. Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case). Since tweets are only collected in discrete, 1-second time intervals, it is natural to consider only the discrete times $t = 1 \text{s}, 2 \text{s}, \ldots, $ relative to a reference time. We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$

@@

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine. We coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour. \textbf{[[Josh: Dave do you think we should talk about why we chose 1-6 and why we chose 10 minutes. If so this would be a good place. I think this is a great explanation however.]] }

>>>>

For the activity-based communities, we consider only the timing of each users tweets and ignore any additional content. From this starting point, we can view the behavior of a user $u$ on Twitter as a point process, where at any instant $t$ the user has either emitted a tweet ($X_{t}(u) = 1$) or remained silent ($X_{t}(u) = 0$). This is the view of a user's dynamics taken in \cite{ver2012information} and \cite{darmon2013understanding}. Thus, we reduce all of the information generated by a user on Twitter to a time series $\{ X_{t}(u)\}$ where $t$ ranges over the time interval for which we have data (9 weeks in this case). Because status updates are only collected in discrete, 1-second time intervals, it is natural to consider the only the discrete times $t = 1 \text{ s}, 2 \text{ s}, \ldots, $ relative to a reference time. We can then compute the flow of information between two users $u$ and $v$ by computing the transfer entropy between their time series $X_{t}(u)$ and $X_{t}(v).$

@@

Operationally, we expect users to interact with Twitter on a human time scale, and thus the natural one-second time resolution is too fine. We coarsen each time series by considering non-overlapping time intervals ten minutes in length. For each time interval, we record a 1 if the user has tweeted during that time interval, and a 0 if they have not. Thus, the new coarsened time series now captures whether or not the user has been active on Twitter over any given ten minute time interval in our data set. We then compute the transfer entropy on these coarsened time series taking $k$ to range from 1 to 6, which corresponds to a lag of ten minutes to an hour. The choice of lag must balance a trade-off between additional information and sparsity of samples: as we increase the lag, we account for longer range dependencies, but we also decrease the number of samples availabe to infer a higher dimensional predictive distribution. Ultimately, due to similarities in the underlying communities (see Figure \ref{Fig-compare_coverings}), we chose a lag-4 transfer entropy. All references to activity-based weights, unless otherwise noted, refer to this choice of lag.
